Extension of the approximate static condensation method for multi-material diffusion problems to 3D

### 2019-10-26 3d/asc3d.tex
Add cyl example images
Add conv table for cylinder
Add spherical inclusion example

\subsection{General example: planar sandwich}

\AZ{TBA: high-contrast $k$, sequence of voronoi and brick meshes (skewed parallel interfaces), compare with homo, plot fluxes}

Pic: $p_h$ + fluxes and error for cyl

@@

\AZ{Mikhail, please correct the details.}
Funded by the Department of Energy at Los Alamos National Laboratory
under contracts DE-AC52-06NA25396 and the DOE Office of Science
Advanced Computing Research (ASCR) program in Applied Mathematical
Sciences. Alexander Zhiliakov acknowledges the internship opportunity in the Los Alamos National Laboratory.

>>>>

\subsection{Planar sandwich}

We choose~$\vect K = k\,\vect I$ with $k = 10^4$ in the middle part of the domain, and $k = 1$ in the left and right parts; $c = 2$, $f = 0$, and $\partial\Omega = \partial\Omega_D$ in~\eqref{dual} and~\eqref{dual:bc}. The exact solution is continuous piecewise linear s.t. its normal flux is also continuous.

\begin{figure}[H]
	\centering
	\begin{subfigure}[t]{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{cyl_sol.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}[t]{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{cyl_err.cropped}.png}
	\end{subfigure}%
	\caption{Left: Computed solution $p_h$ and the flux. Right: error $(p - p_h)$. Here~$\|p - p_h\|_{\lTwoSpace} = 1.77\times 10^{-4}$}
	\label{fig:cyl}		
\end{figure}

\begin{table}[H]
	\centering\footnotesize
	\caption{Convergence results for the cylinder example. $\bar q$ denotes the mean value of a function~$q$} 
	\label{tab:cyl}
	\begin{subtable}{1.\linewidth}
		\centering
		\begin{tabular}[1.2]{|c||c|c||c||c|}
			\hline
			$h$ & $\| p - p_h \|_{\lTwoSpace}$ & Order & $| \bar p - \bar p_h |$ & $\| p - p_h \|_{\infty}$ \\ 
			\hline
			\input{cyl_table.tex}
		\end{tabular}
	\end{subtable}%
\end{table}

\AZ{TBA: compare with homo. methods}

\subsection{Spherical inclusion}

We choose~$\vect K = k\,\vect I$ with $k = 1$ inside the sphere and $k = 100$ outside; $c = 1$ and $\partial\Omega = \partial\Omega_D$ in~\eqref{dual} and~\eqref{dual:bc}. The exact solution is set to be continuous piecewise quadratic s.t. its normal flux is also continuous across the interface. Load data~$f$ is computed from the exact solution.

\begin{figure}[H]
	\centering
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl100.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl1000.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl10000.cropped}.png}
	\end{subfigure}%
	\vskip .3cm
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl100_k.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl1000_k.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw[.9]{{incl10000_k.cropped}.png}
	\end{subfigure}
	\caption{Spherical material inclusion for $h \in \{ 6.44\times 10^{-1}, 2.97\times 10^{-1}, 1.53\times 10^{-1}\}$ resulting from Tangram moment-of-fluid interface reconstruction. Note that the interface is discontinuous}
	\label{fig:incl}		
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{sph_p_1000.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{sph_e_1000.cropped}.png}
	\end{subfigure}%
	\vskip .3cm
	\begin{subfigure}{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{sph_p_10000.cropped}.png}
	\end{subfigure}%
	\begin{subfigure}{.5\linewidth}
		\centering
		\includegraphicsw[.9]{{sph_e_10000.cropped}.png}
	\end{subfigure}%	
	\caption{Computed solution $p_h$ and corresponding error~$(p - p_h)$, $h = 2.97\times 10^{-1}$ (Top) and $h = 1.53\times 10^{-1}$ (Bottom)}
	\label{fig:sph}		
\end{figure}

\begin{table}[H]
	\centering\footnotesize
	\caption{Convergence results for the spherical inclusion example. $\bar q$ denotes the mean value of a function~$q$} 
	\label{tab:cube}
	\begin{subtable}{1.\linewidth}
		\centering
		\begin{tabular}[1.2]{|c||c|c||c||c|}
			\hline
			$h$ & $\| p - p_h \|_{\lTwoSpace}$ & Order & $| \bar p - \bar p_h |$ & $\| p - p_h \|_{\infty}$ \\ 
			\hline
			\input{cube_table.tex}
		\end{tabular}
	\end{subtable}%
\end{table}

We see that for this example the reconstructed interface is actually discontinuous, and the convergence rate for pressure $\lTwoSpace$-error is worse than for piecewise linear case (where the interface is reconstructed exactly), cf. Tables~$\ref{tab:cyl}$ and \ref{tab:cube}. However, in both cases convergence rate is close to one. We see that $\ell^\infty(\Omega)$-error is sensitive to small isolated material volumes that appear to have ``wrong'' material ID after the interface reconstruction (similar to what we observe for 2D case, cf.~\cite[Section~4.3.1]{ZHILIAKOV2019333}); however, this does not affect the $\lTwoSpace$-error.

@@

This work was performed under the auspices of the National Nuclear Security Administration of the US Department of Energy at Los Alamos National Laboratory under Contract No.~89233218CNA000001. The authors gratefully acknowledge the support of the NNSA Advanced Simulation and Computing ASC) Program.
